General exp analysis -- 4/18/2018

### 2018-04-29 resistingrhythm/analysis/paper_figures.Rmd
Merged burst and sustained E figures

# Figure 2. Sustained E

```{r, fig.width=3.0, fig.height=2.0}
shift <- -0.15

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

@@

# -
layout_matrix <- rbind(
  c(NA, 7, 7, 8, 8),
  c(5, 1, 1, 2, 2), 
  c(5, 1, 1, 2, 2), 
  c(5, 1, 1, 2, 2), 
  c(5, 1, 1, 2, 2), 
  c(6, 3, 3, 4, 4),
  c(6, 3, 3, 4, 4),
  c(6, 3, 3, 4, 4),
  c(6, 3, 3, 4, 4)
)

# -
png(file="fig2.png", bg="white", width=6.0, height=4.0, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=layout_matrix)
dev.off()

# Figure 3. Burst E

```{r, fig.width=2.25, fig.height=2}
shift <- -0.15

# --------------------------------------------------------
# Var
results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="a.", y="Variance (s)", x="Osc. rate (Hz)") +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p1

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="b.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p2

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  lims(y=c(-3, 3)) +
  scale_color_manual(values=c("dodgerblue3", "black"), guide=FALSE) +
  stat_compare_means(method="wilcox.test", label="p.signif", label.x=1.3, size=3) +
  theme(
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.6, size=18, face="bold")) -> p5

p3 <- textGrob("Synchrony")
p4 <- textGrob("Excitability")

layout_matrix <- rbind(
  c(3, 1, 1, NA), 
  c(3, 1, 1, NA), 
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(NA, NA, NA, 5))

# -
png(file="fig3.png", bg="white", width=4.5, height=4.0, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()

rm(p1, p2, p3, p4, p5)

# -
print(wilcox.test(x=(tmp3$rate_k - tmp3$rate_ref), y=(tmp4$rate_k - tmp4$rate_ref)))
```

# Figure 4. Weak E oscillations, variance, and error.

@@

# -
png(file="fig4.png", bg="white", width=4.8, height=3.3, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()

@@

# Figure 5. Sustained I

@@

# -
png(file="fig5.png", bg="white", width=6, height=4.4, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=layout_matrix)
dev.off()

@@

# Figure 6. Variable Calcium targets and sustained E

@@

# p3 <- textGrob("Homeostatsis")
p3 <- textGrob("Synchrony")
p4 <- textGrob("Excitability    ")

@@

# -
png(file="fig6.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()

>>>>

# Figure 2. Sustained and burst E

```{r, fig.width=4.5, fig.height=2.0}
shift <- -0.15

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(0, 70)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.25, size=18, face="bold")) -> p3

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05)) +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8) +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), width=.15, size=0.2) +
  # geom_boxplot(size=0.3, outlier.colour = NA, alpha=0.5) +
  labs(title="e.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(-4, 4)) +
  geom_hline(yintercept=0, size=0.2) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

@@

# --------------------------------------------------------
# Bursts

# Var
results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=mse_var, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="c.", y="Variance (s)", x="Osc. rate (Hz)") +
  theme_classic() + 
  lims(y=c(0, .01)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="d.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="f.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.1, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

# NEW

# -
layout_matrix <- rbind(
  c(NA, 8, 8, 9, 9, 9, 9, NA),
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, NA), 
  c(10, 1, 1, 2, 2, 5, 5, 7), 
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7),
  c(11, 3, 3, 4, 4, 6, 6, 7)
)

p8 <- textGrob("No homeostatsis")
p9 <- textGrob("Homeostatsis")
p10 <- textGrob("Synchrony")
p11 <- textGrob("Excitability")

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)

# -
png(file="fig2.png", bg="white", width=9.0, height=4.0, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
dev.off()
```

```{r}
print(wilcox.test(x=(tmp3$rate_k - tmp3$rate_ref), y=(tmp4$rate_k - tmp4$rate_ref)))
```

# Figure 3. Weak E oscillations, variance, and error.

@@

# -
png(file="fig3.png", bg="white", width=4.8, height=3.3, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()

@@

# Figure 4. Sustained I

@@

# -
png(file="fig4.png", bg="white", width=6, height=4.4, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, layout_matrix=layout_matrix)
dev.off()

@@

# Figure 5. Variable Calcium targets and sustained E

@@

# p3 <- textGrob("Homeostatsis")
p3 <- textGrob("Synchrony")
p4 <- textGrob("Excitability")

@@

# -
png(file="fig5.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()
